First steps in synthetic algebraic geometry

### 2017-03-20 snippets/injective.tex
typo

\begin{proof}
The implication~``1~$\Rightarrow$~2'' is trivial. The converse direction uses a
typical argument with Zorn's lemma, considering a maximal extension. The
equivalence~``$2~\Leftrightarrow~3$'' is routine, using the Kripke--Joyal
semantics to interpret the internal statement. Condition~4 is a straightforward
reformulation of condition~3.
\end{proof}

@@

\begin{rem}The object~$\P_{\leq 1}(\F)$ of subsingletons of $\F$ can be
interpreted as the object of \emph{partially-defined
elements} of $\F$. In this view, the empty subset is the maximally undefined
element and a singleton is a maximally defined element. The proposition shows
that~$\F$ is flabby if and only if any such partially-defined element can be
refined to an honest element of~$\F$.\end{rem}

@@

Let~$K \subseteq \G$ be a subsingleton. We consider the injectivity diagram
\[ \xymatrix{
  m[\E] \cup \F' \ar[r]\ar[d] & \F \ar@{-->}[ld] \\
  \I,
} \]
where~$\F' \defeq \{ s \? \F \,|\, \text{$K$ is inhabited} \}$ and the solid
vertical arrow is defined in the following way: It should map an element~$s \in
\F'$ to~$k'(s)$, where~$k'$ is any element of~$K$; and it should map an
element~$m[u] \in m[\E]$ to~$k(u)$. These prescriptions determine a well-defined
map.

@@

@@

\begin{lemma}A sheaf of set or a sheaf of modules is injective if and only if it
is locally injective.\end{lemma}

@@

\begin{rem}The \emph{Godement construction} is a well-known way of embedding an
inhabited sheaf of sets~$\F$ into an injective sheaf, namely embedding it into
the sheaf of not necessarily continuous sections of the étale space of~$\F$:
\[ U \subseteq X \quad\longmapsto\quad
  \prod_{x \in U} \F_x. \]
The sheaf~$\P_{\leq1}(\F)$ does not coincide with this construction.
Instead, it is the sheaf with
\[ U \subseteq X \quad\longmapsto\quad
  \{ \langle V, s \rangle \,|\,
    \text{$V \subseteq U$ open, $s \in \F(V)$} \}. \]
It's not possible to describe the Godement construction in the internal language
of~$\Sh(X)$, since in the Godement construction the underlying set of~$X$
enters. But the sheaf topos of~$X$ doesn't remember this set. For instance, let~$X$
be an inhabited indiscrete topological space. Then~$\Sh(X)$ is equivalent
to~$\Set$.
\end{rem}

>>>>

\begin{proof}
The implication~``1~$\Rightarrow$~2'' is trivial. The converse direction uses a
typical argument with Zorn's lemma, considering a maximal extension. The
equivalence~``$2~\Leftrightarrow~3$'' is routine, using the Kripke--Joyal
semantics to interpret the internal statement. Condition~4 is a straightforward
reformulation of Condition~3.
\end{proof}

@@

The object~$\P_{\leq 1}(\F)$ of subsingletons of $\F$ can be
interpreted as the object of \emph{partially-defined
elements} of $\F$. In this view, the empty subset is the maximally undefined
element and a singleton is a maximally defined element. The proposition shows
that~$\F$ is flabby if and only if any such partially-defined element can be
refined to an honest element of~$\F$.

@@

Let~$K \subseteq \G$ be a subsingleton. We consider the injectivity diagram
\[ \xymatrix{
  m[\E] \cup \F' \ar@{^{(}->}[r]\ar[d] & \F \ar@{-->}[ld] \\
  \I,
} \]
where~$\F' \defeq \{ s \? \F \,|\, \text{$K$ is inhabited} \}$ and the solid
vertical arrow is defined in the following way: It should map an element~$s \in
\F'$ to~$k'(s)$, where~$k'$ is any element of~$K$; and it should map an
element~$m[u] \in m[\E]$ to~$k(u)$. These prescriptions determine a well-defined
map.

@@

% XXX: Remark that proof requires AxC and that it's a unique feature of sheaf toposes.
% Counterexample?

@@

\begin{lemma}A sheaf of sets or a sheaf of modules is injective if and only if it
is locally injective.\end{lemma}

@@

\begin{rem}The \emph{Godement construction} is a well-known way of embedding an
inhabited sheaf of sets~$\F$ into an injective sheaf, namely embedding it into
the sheaf of not necessarily continuous sections of the étale space of~$\F$:
\[ U \subseteq X \quad\longmapsto\quad
  \prod_{x \in U} \F_x. \]
The sheaf~$\P_{\leq1}(\F)$ does not coincide with this construction.
Instead, it is the sheaf with
\[ U \subseteq X \quad\longmapsto\quad
  \{ \langle V, s \rangle \,|\,
    \text{$V \subseteq U$ open, $s \in \F(V)$} \}. \]
It's not possible to describe the Godement construction in the internal language
of~$\Sh(X)$, since in the Godement construction the underlying set of~$X$
enters. But the sheaf topos of~$X$ doesn't remember this set. For instance, if~$X$
is an inhabited indiscrete topological spac, then~$\Sh(X)$ is equivalent
to~$\Set$.
\end{rem}
